CPP_analysis

### 2019-10-02 CPP_analysis.Rmd
Renamed columns in different files for consistency; made maps

```{r CPP_calc_2008}
DI_summary_2008<-data.frame(read.csv("CPP_2008.csv"))
d.model.fit.2008 <- drm(DI ~ PP, data = DI_summary_2008, curveid = POP, fct = LL.5())

@@

```{r collate_cpp_values}
cpp_2019<-data.frame(ED(d.model.fit, 50))
cpp_2019<-rownames_to_column(cpp_2019, var="pop") 
cpp_2019$pop<-str_sub(cpp_2019$pop,3,5)
popdata_2019<-DI_summary %>% group_by(pop) %>% 
  summarize(lat=first(lat), country=first(country))
cpp_2019<-right_join(cpp_2019, popdata_2019, by="pop")
#drop PBS from this list for now; CPP estimate doesn't make sense
#cpp_2019<-filter(cpp_2019, pop!="PBS")
cpp_2019$year<-rep("2019", nrow(cpp_2019))

cpp_2008<-data.frame(ED(d.model.fit.2008, 50)) %>% rownames_to_column(var="pop")
cpp_2008$pop<-str_sub(cpp_2008$pop,3,5)
popdata_2008<-DI_summary_2008 %>% group_by(POP) %>% 
  summarize(lat=first(LAT), country=first(COUNTRY), year=first(YEAR)) 
colnames(popdata_2008)[1]<-"pop"
cpp_2008<-right_join(cpp_2008, popdata_2008, by="pop")

cpp_1988<-data.frame(read.csv("CPP_1988.csv")) 
cpp_1988$pop<-na_if(cpp_1988$pop, "NA")
cpp_1988$Std..Error<-na_if(cpp_1988$Std..Error, "NA")

@@

```{r Japan_US_years}
ggplot(cpp_2, aes(x=lat, y=Estimate, fill=year, color=year)) + 
  scale_color_manual(values=c("white","gray","black")) + 
  scale_fill_manual(values=c("white","gray","black"))+ 
  geom_point(shape=21, color="black") + 
  geom_errorbar(aes(ymin=Estimate-Std..Error, ymax=Estimate+Std..Error), na.rm=TRUE) + 
  facet_grid(~country) + stat_smooth(method=lm, se=FALSE)
```
```{r }
ggplot(cpp_2, aes(x=lat, y=Estimate, color=country)) + 
  geom_point() + 
  geom_errorbar(aes(ymin=Estimate-Std..Error, ymax=Estimate+Std..Error), na.rm=TRUE) + 
  facet_grid(~year) + stat_smooth(method=lm, se=FALSE)
```

```{r incidence_lat_year}
DI_short_2008<-filter(DI_summary_2008, PP==8)
names(DI_short_2008)<-c("pop","country","lat","pp","year","DI")

DI_short_2018<-filter(DI_summary, pp==8) %>% group_by(pop) %>% 
  summarize(country=first(country), lat=first(lat), pp=first(pp), emb=sum(emb), total=sum(total))
DI_short_2018$DI<-DI_short_2018$emb/DI_short_2018$total
DI_short_2018<-DI_short_2018[,c(1:4,7)] 
DI_short_2018$year<-rep("2018",nrow(DI_short_2018))
DI_short_2018<-DI_short_2018[,c(1,2,3,4,6,5)]

DI_short_2<-rbind(DI_short_2008, DI_short_2018)

>>>>

```{r CPP_calc_2008}
DI_summary_2008<-data.frame(read.csv("CPP_2008.csv"))
d.model.fit.2008 <- drm(DI ~ photoperiod, data = DI_summary_2008, curveid = pop, fct = LL.5())

@@

```{r collate_cpp_values}
cpp_2019<-data.frame(ED(d.model.fit, 50))
cpp_2019<-rownames_to_column(cpp_2019, var="pop") 
cpp_2019$pop<-str_sub(cpp_2019$pop,3,5)
popdata_2019<-DI_summary %>% group_by(pop) %>% 
  summarize(lat=first(lat), country=first(country))
cpp_2019<-right_join(cpp_2019, popdata_2019, by="pop")
cpp_2019$year<-rep("2019", nrow(cpp_2019))
colnames(cpp_2019)[colnames(cpp_2019)=="Std..Error"] <- "StdError"

cpp_2008<-data.frame(ED(d.model.fit.2008, 50)) %>% rownames_to_column(var="pop")
cpp_2008$pop<-str_sub(cpp_2008$pop,3,5)
colnames(cpp_2008)[colnames(cpp_2008)=="Std..Error"] <- "StdError"
popdata_2008<-DI_summary_2008 %>% group_by(pop) %>% 
  summarize(country=first(country), lat=first(lat), year=first(year)) 
#colnames(popdata_2008)[1]<-"pop"
cpp_2008<-right_join(cpp_2008, popdata_2008, by="pop")

cpp_1988<-data.frame(read.csv("CPP_1988.csv")) 
cpp_1988$pop<-na_if(cpp_1988$pop, "NA")
cpp_1988$StdError<-na_if(cpp_1988$StdError, "NA")

@@

```{r Japan_US_years}
ggplot(cpp_2, aes(x=lat, y=Estimate, fill=year, color=year)) + 
  scale_color_manual(values=c("white","gray","black")) + 
  scale_fill_manual(values=c("white","gray","black"))+ 
  geom_point(shape=21, color="black") + 
  geom_errorbar(aes(ymin=Estimate-StdError, ymax=Estimate+StdError), na.rm=TRUE) + 
  facet_grid(~country) + stat_smooth(method=lm, se=FALSE)
```
```{r }
ggplot(cpp_2, aes(x=lat, y=Estimate, color=country)) + 
  geom_point() + 
  geom_errorbar(aes(ymin=Estimate-StdError, ymax=Estimate+StdError), na.rm=TRUE) + 
  facet_grid(~year) + stat_smooth(method=lm, se=FALSE)
```

```{r incidence_lat_year}
DI_short_2008<-filter(DI_summary_2008, photoperiod==8)

#unnecessary renaming between pp/photoperiod - harmonize @ beginning?
DI_short_2018<-filter(DI_summary, pp==8) %>% group_by(pop) %>% 
  summarize(country=first(country), lat=first(lat), photoperiod=first(pp), emb=sum(emb), total=sum(total))
DI_short_2018$DI<-DI_short_2018$emb/DI_short_2018$total
DI_short_2018<-DI_short_2018[,c(1:4,7)] 
DI_short_2018$year<-rep("2018",nrow(DI_short_2018))

DI_short_2<-rbind(DI_short_2008, DI_short_2018)
write_csv(DI_short_2, "diapause_incidence_8h_2008_2018.csv")
